Automatic extraction of network signatures from malware code

### 2016-10-10 paper.tex
Started challenges

\begin{abstract}
Hello
\end{abstract}

@@

\section{Challenges}

>>>>

\begin{abstract}

\end{abstract}

@@

\section{Challenges}
We abstract the problem to the following: given a program point,
can we automatically provide an ordered set of symbolic packets 
that must be received (and sent) by the client such that the program 
reaches the program point. The symbolic packets can be used as
network signatures and used to detect malware (a set of packets
satisfying the symbolic packets in order will infer that there 
is a malware with high confidence). By constructing symbolic packet
signatures, we can generalise the intrusion policy and reduce 
true negatives.
